### 2020-12-14 paper/sex_selection_spacing-ver5.tex
Discuss period vs cohort fertility in more detail

% Questions addressed and why valuable
The main question I address here is how birth spacing responded to these changes, 
especially the spread of sex selection. 
The motivation is twofold.
First, the growing use of sex-selective abortions may substantially increase birth spacing
because, as detailed below, it takes 6 months or more after an abortion to reach the same 
point in the next pregnancy.
However, researchers have failed to appreciate this effect, and we do not know the size of 
the impact.
Second, greater educational attainment by women, higher household income, and the low and 
declining female labor force participation all likely influence birth spacing. 
Thus, the combined changes in birth spacing may outpace what we have observed in 
other countries.

@@

First, did changes in birth spacing bias the fertility estimates for India? 
With longer spacing, mothers will be older at each parity, and this tempo effect makes the 
total fertility rate a downward-biased estimate of cohort fertility
\citep{Hotz1997,Bongaarts1999,Ni-Bhrolchain2011}. 
Hence, if birth intervals increased substantially, then India's fertility may be higher 
than generally accepted.

>>>>

% Questions addressed and why valuable
The main question I address here is how birth spacing responded to these changes, 
especially the spread of sex selection. 
The motivation is twofold.
First, past research has failed to appreciate that the growing use of sex-selective 
abortions may substantially increase birth spacing; as detailed below, it takes 6 months 
or more after an abortion to reach the same point in the next pregnancy.
Second, women's greater educational attainment, higher household income, but low and 
declining female labor force participation all likely influence birth spacing. 
The combination of the increasing use of sex selection and the other societal changes 
can significantly impact birth spacing, but we know little about how much.

@@

First, did changes in birth spacing make us overestimate the decline in cohort fertility?
With longer spacing, mothers will be older at each parity, and this tempo effect 
makes period fertility measures, such as the total fertility rate, downward-biased
estimates of cohort fertility \citep{Hotz1997,Bongaarts1999,Ni-Bhrolchain2011}.
Hence, a rapidly expanding use of sex selection could make the total fertility rate---our 
most used fertility measure---fall substantially faster than cohort fertility.
In this case, households' fertility goals may be higher than generally accepted.
